\ttitle

### 2015-08-23 Chapters/CRP_Complications.tex
Review 1
- Every sentence on a new line
- Fits my OCD
Review 1 - CRP_Complications
- Major tidying up
- References and spell checked
- Compiles ok
- HAVE NOT CHECKED BAD BOXES, TITLES, ETC.

\section{Methods}
\todo{Check dates for this study}
Patients who underwent elective pancreaticoduodenectomy between January 2008 and July 2012 were included in this study. Patients who underwent only a trial dissection or trial dissection and surgical bypass during this period were excluded. All patients were given antibiotic prophylaxis at induction and this was continued for 24 hours after surgery. All patients had general anaesthesia supplemented either with patient-controlled epidural analgesia or spinal diamorphine and patient-controlled opiate analgesia for postoperative pain relief. Octreotide (200$\mu$g) was administered subcutaneously three times a day for 5 days in all patients and continued longer in patients diagnosed with a postoperative pancreatic fistula. Patients were routinely admitted to the surgical high dependency unit where a standardised regimen was followed for early mobilisation, chest physiotherapy and early enteral nutrition. All patients had one or two surgical drain(s) placed at the time of surgery which were removed at the clinician's discretion during the postoperative period based on the presence or absence of postoperative pancreatic fistula or other intra-abdominal collections.

@@

\todo{Complete this section - most of this can be modified from the stats sections in other chapters}

\section{Results}
\subsection{POPF, infective complications and other outcomes}
Pancreaticoduodenectomy was performed in 188 patients (126 male, 67\%) during the study period. The median age was 63.5 years (IQR 54 - 70 years). 79 (42\%) patients were over the age of 65 years.

@@

%Quick analysis of CPET vs postop CRP - maybe one table
%ROC analysis of CRP vs LOS
%Multivariate analysis of CRP as continuous or categorical vs complications, 
\clearpage
\section{Discussion}

The results of the present study show that the severity of the postoperative systemic inflammatory response as measured by serial serum CRP levels in the first week is associated with postoperative complications after pancreaticoduodenectomy. While numerous studies have reported on a variety of methods to predict as well as diagnose POPF, few have reported on the role of CRP in predicting complications other than POPF.

The introduction of the ISGPF definition for POPF has made the diagnosis of this complication simple and uniform. The rate of POPF before the standardised definition was introduced varied anywhere between 2\% and 40\%. However, in the post-ISGPF era, the rate of POPF in published literature has remained approximately 25\%. The sole criterion for the diagnosis of POPF is a drain amylase content on or after the third postoperative day three times the upper limit of normal for serum amylase in the testing laboratory.

@@

\todo{straatman_predictive_2015 - This is hot-off the press - reference this}

>>>>

\clearpage
\section{Methods}

Patients who underwent elective pancreaticoduodenectomy between January 2008 and July 2012 were included in this study. 
Patients who underwent only a trial dissection or trial dissection and palliative surgical bypass during this period were excluded. 
All patients were given antibiotic prophylaxis at induction and this was continued for 24 hours after surgery. 
All patients had general anaesthesia supplemented either with patient-controlled epidural analgesia or spinal diamorphine and patient-controlled opiate analgesia for postoperative pain relief. 
Octreotide (200$\mu$g) was administered subcutaneously three times a day for 5 days in all patients and continued longer in patients diagnosed with a postoperative pancreatic fistula. 
Patients were routinely admitted to the surgical high dependency unit where a standardised regimen was followed for early mobilisation, chest physiotherapy and early enteral nutrition. 
All patients had one or two surgical drain(s) placed at the time of surgery which were removed at the clinician's discretion during the postoperative period based on the presence or absence of postoperative pancreatic fistula or other intra-abdominal collections.

@@

\clearpage
\section{Results}
\subsection{POPF, infective complications and other outcomes}
Pancreaticoduodenectomy was performed in 188 patients (126 male, 67\%) during the study period. 
The median age was 63.5 years (IQR 54 - 70 years). 79 (42\%) patients were over the age of 65 years.

@@

\clearpage
\section{Discussion}

The results of the present study show that the severity of the postoperative systemic inflammatory response as measured by serial serum CRP levels in the first week is associated with postoperative complications after pancreaticoduodenectomy. 
The results also demonstrate that postoperative CRP trends are more useful in predicting infective complications in patients who did not develop a post-operative pancreatic fistula.

While numerous studies have reported on a variety of methods to predict as well as diagnose POPF, few have reported on the role of CRP in predicting complications other than POPF.

The introduction of the ISGPF definition for POPF has made the diagnosis of this complication simple and uniform \parencite{bassi_postoperative_2005}.
The rate of POPF before the standardised definition was introduced varied anywhere between 2\% and 40\%. 
However, in the post-ISGPF era, the rate of POPF in published literature has remained approximately 25\% \parencite{knight_evaluation_2010}. 
The sole criterion for the diagnosis of POPF is a drain amylase content on or after the third postoperative day three times the upper limit of normal for serum amylase in the testing laboratory \parencite{bassi_postoperative_2005} .

@@

\todo{his is hot-off the press - reference this}%straatman_predictive_2015 - T
